\LARGE \bf Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty

### 2014-10-03 paper.tex

\begin{abstract}
Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object defined by a Gaussian process implicit surface (GPIS), but the method is applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass and use these solve the associated MAB model, finding that it computes grasps of similar quality and can reduce computation time by an order of magnitude.  This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
\end{abstract}

@@

\section{Problem Definition}
Before we present the problem definition, we introduce the our grasping model, the line of action.

\subsection{Line of action}
Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide01.jpg}
\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
\vspace*{-10pt}
\label{fig:line_of_action}
\end{figure}

>>>>

\begin{abstract}
Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object defined by a Gaussian process implicit surface (GPIS), but the method is applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass and use these solve the associated MAB model, finding that it computes grasps of similar quality and can reduce computation time by an order of magnitude.  This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
\end{abstract}

@@

\section{Preliminaries and Problem Definition}
Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.

Since we are in an uncertain environment, we are interested in calculating the expected quality, or $E(Q)$. $E(Q)$ is computed by sampling from our distributions on pose, shape or material properties (friction coefficient or density) and averaging the qualities that are computed. Reducing the time to do this for a large number of grasps is the primary focus of the paper.

\subsection{Line of action}
In an uncertain environment one wouldn't actually know the true $g$, thus we have to work with the trajectory of the gripper. Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 4cm]{figures/Slide01.jpg}
\caption{Illustration of a grasp plan $\Gamma$ composed of two lines of action, $\gamma_1(t)$ and $\gamma_2(t)$}
\vspace*{-10pt}
\label{fig:line_of_action}
\end{figure}
